Ear canal dynamic motion piezoelectric energy harvester using a bistable oscillator cycled by coupled hydraulic switches made of collapsed flexible tubes.

### 2022-09-29 article_system.tex
update

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{SYSTEM GLOBAL MODELING AND SIMULATIONS}
\label{sec:SYSTEM MODELING AND SIMULATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
The harvester is a multyphisic system composed of hydraulic, mechanical, and electrical components. This section presents a global multiphysic model describing the theoretical system operation. Two coupled subsystems are considered. The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BO + APG) under the mechanical influence of a HV and a HC. Then, the subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug. Finally, the section \ref{subsec:Global model simulation} exposes the numerical simulation of the designed multiphysic coupled model.

@@

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\label{NUMERICAL MODEL AND SIMULATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

	%///////////////////////////////////////////// 
	\subsection{HV hydraulic targeted behavior}	
	\label{subsec:HV hydraulic targeted behavior}
	%/////////////////////////////////////////////
A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs. The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation. In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. So we introduce $r_{Cf}$ as follows:
\begin{equation}
	r_{Cf} = \dfrac{\text{Closed HV}}{\text{Opened HV}}	= \dfrac{Cf_c}{Cf_0}	
	\label{eq:r_Cf_definition}
\end{equation}
Where $Cf_f=Cf(\pm x_0)$. The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube. Therefore, we preliminarily assume that it is linear and defined as follows :
\begin{align}
	Cf(x_m) & = Cf_0 + \dfrac{Cf_f - Cf_0}{x_0}\ x_m  \notag \\
			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
			\label{eq:Cf(x_m)_linear}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={9.5cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_debit_Cf_pression_1CYCLE.pdf}
	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
	\label{fig:simu_pos_debit_Cf_pression_1CYCLE}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={10cm 0cm 0cm 0cm},clip, width=0.7\textwidth]{figures/simu_pos_Up_puissances_energie_1CYCLE.pdf}
	\caption{$K_{HV}$ impact on the evolution of the BO mass potential energy.}
	\label{fig:simu_pos_Up_puissances_energie_1CYCLE}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{EXPERIMENTAL CHARACTERIZATIONS}
\label{sec:EXPERIMENTAL CHARACTERIZATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter}	
	\label{The electromechanical converter}
    %/////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
\begin{center}
\captionsetup{justification=centering}
	\begin{subfigure} [h!]{0.49\textwidth}
		\includegraphics[trim={1.4cm 0cm 0cm 0cm},clip,width=\textwidth]{figures/monobloc+GPA_face.pdf}
		\caption{aaa} 
		\label{fig:/monobloc+GPA_face}
	\end{subfigure}
	%\hfill
	\begin{subfigure}[h!]{0.49\textwidth}
		\includegraphics[trim={6cm 3cm 7.5cm 2.6cm},clip, width=\textwidth]{figures/monobloc+GPA_iso.pdf}
		\caption{aaa}  
		\label{fig:/monobloc+GPA_iso}
	\end{subfigure}
	\caption{aaa}
\end{center}
\label{fig:/monobloc+GPA_face}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

    %///////////////////////////////////////////// 
	\subsection{The HV hydraulic behavior}	
	\label{The hydraulic valves}
    %/////////////////////////////////////////////
	\subsubsection{Test bench presentation}
	\subsubsection{Results and discussion}

>>>>

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{SYSTEM GLOBAL MODELING}
\label{sec:SYSTEM MODELING}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
The harvester is a multyphisic system composed of hydraulic, mechanical, and electrical components. This section presents a global multiphysic model describing the theoretical system operation. Two coupled subsystems are considered. The subsection \ref{subsec:The electromechanical converter} shows the modeling of the electromechanical frequency-up converter (BO + APG) under the mechanical influence of a HV and a HC. Then, the subsection \ref{subsec:The hydraulic circuit} discusses the design of the hydraulic circuit composed of the two HVs, the two HCs, the hydraulic amplifier, the pressure separator and the liquid filled earplug. Finally, the section \ref{subsec:Global model simulation} exposes the numerical simulation of the designed multiphysic coupled model.

@@

%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{NUMERICAL MODEL AND SIMULATIONS}
\label{NUMERICAL MODEL AND SIMULATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%

	%///////////////////////////////////////////// 
	\subsection{Targeted hydraulic behavior of the HVs}	
	\label{subsec:HV hydraulic targeted behavior}
	%/////////////////////////////////////////////
A multiphysic coupled model has been established with the equations and the preliminary dimensioning previously introduced. The unknown key aspect stays the hydraulic behavior $Cf(x_m)$ of the HVs. The numerical resolution of the differential equations can provide the necessary condition to satisfy in order to perform the adequate hydraulic commutation. In fact, the ratio between the pressure loss coefficient of the closed HV and the one of the opened HV has to be sufficient to force the flow through the opened branch. So we introduce $r_{Cf}$ as follows:
\begin{equation}
	r_{Cf} = \dfrac{Cf(\text{Closed HV})}{Cf(\text{Opened HV})}	= \dfrac{Cf_c}{Cf_0}	
	\label{eq:r_Cf_definition}
\end{equation}
Where $Cf_c=Cf(\pm x_0)$. The literature does not provide the constitutive relation between $x_m$ and $Cf$ for a buckled flexible tube. Therefore, we preliminarily assume that it is linear and defined as follows :
\begin{align}
	Cf(x_m) & = Cf_0 + \dfrac{Cf_c - Cf_0}{x_0}\ x_m  \notag \\
			& = Cf_0 \Biggl( 1 + \biggl(\dfrac{1}{r_{Cf}-1} \biggr)\dfrac{x_m}{x_0} \Biggr)
			\label{eq:Cf(x_m)_linear}
\end{align}
Regarding the BO symmetry, the relation between $Cf$ and $x_m$ has to be an even function to allow the system cycling, i.e. $Cf(x_m) = Cf(-x_m)$.

	%///////////////////////////////////////////// 
	\subsection{Simulation results}	
	\label{subsec:Simulation results}
	%/////////////////////////////////////////////
The numerical model aims to demonstrate the theoretical operation of the new concept of harvester. By imposing a volume variation $\Delta V_{ear}(t)$ recorded during the mastication cycle of a human subject (fig. \ref{fig:deltaV_ear}), the numerical model must give the theoretical temporal evolution of the hydraulic, mechanic and electric coupled parameters defining the harvester.

The ratio $r_{Cf}$ has been increased until it was sufficient to prioritize the flow through the opened HV. The mastication cycle is identically quadrupled in order to test the system cycling robustness. Also, the earplug is assumed as a perfect flow rate source.

Figure \ref{fig:positions+DeltaV_debits_pear} presents the simulation results, for four identical consecutive mastication cycles, of the mass and the HC pistons positions overplayed with $\Delta V_{ear}(t)$, the flow rates in the two parallel branches and the earplug pressure. The two different sides are identified on the curves by the indexes $t$ for \emph{"top"} side ($x>0$) and $b$ for \emph{"bottom"} side ($x<0$), knowing that the gravity influence is not considered. The same figure shows a focused view on the two main phases of the harvester operation during the actuation by the \emph{"bottom"} HC. The simulation begins with the following initial conditions:
\begin{itemize}
	\item The mass is at the $-x_0$ equilibrium position.
	\item The \emph{"top"} HV is closed ($Cf_{top} = Cf_c$) and the \emph{"bottom"} side HV is opened ($Cf_{bot} = Cf_0$).
	\item There is no contact between the mass and the HCs.
	\item A mastication occurs.
\end{itemize}

The first phase consists on pushing on the BO mass to store potential energy, until the mass reaches $x=0$. During this phase, the fluid exciting the earplug is mostly guided toward the \emph{"bottom"} HC and the earplug pressure is generated by the BO counter-reaction force. The second phase begins after the mass crosses the $x_m=0$ position. The \emph{"top"} HV then opens ($Cf_{top} = Cf_0$) and the \emph{"bottom"} side HV closes ($Cf_{bot} = Cf(x_m)>Cf_0$). The fluid is then preferably guided toward the \emph{"top"} side and the contact between the mass and the HCs is non-existent. The mass goes oscillate around the opposite stable equilibrium position $x_0$ while a part on the oscillatory mechanical energy is converted in electricity by the APG. The cycling of the hydraulic branches is possible when $r_{Cf} =(r_{Cf})_{min}=26$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.5cm},clip, width=\textwidth]{figures/positions+DeltaV_debits_pear.pdf}
	\caption{}
	\label{fig:positions+DeltaV_debits_pear}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={0cm 0cm 0cm 0.9cm},clip, width=\textwidth]{figures/positions_Up_puissances_energies.pdf}
	\caption{}
	\label{fig:positions_Up_puissances_energies}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
\section{EXPERIMENTAL CHARACTERIZATIONS}
\label{sec:EXPERIMENTAL CHARACTERIZATIONS}
%/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\/!\%
    %///////////////////////////////////////////// 
	\subsection{The electromechanical converter}	
	\label{The electromechanical converter}
    %/////////////////////////////////////////////
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
\begin{center}
\captionsetup{justification=centering}
	\begin{subfigure} [h!]{0.49\textwidth}
		\includegraphics[trim={1.4cm 0cm 0cm 0cm},clip,width=\textwidth]{figures/monobloc+GPA_face.pdf}
		\caption{aaa} 
		\label{fig:/monobloc+GPA_face}
	\end{subfigure}
	%\hfill
	\begin{subfigure}[h!]{0.49\textwidth}
		\includegraphics[trim={6cm 3cm 7.5cm 2.6cm},clip, width=\textwidth]{figures/monobloc+GPA_iso.pdf}
		\caption{aaa}  
		\label{fig:/monobloc+GPA_iso}
	\end{subfigure}
	\caption{aaa}
\end{center}
\label{fig:/monobloc+GPA_face}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!htbp]
	\centering
	\captionsetup{justification=centering}
	\includegraphics[trim={1cm 3cm 2cm 2.5cm},clip,width=0.45\textwidth]{figures/BDT_OB+GPA.pdf}
	\caption{Vue de face de GPA et l’OB monobloc sur le banc de caractérisation
	électromécanique.}
	\label{fig:BDT_OB+GPA}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
\begin{table}[!htbp]
\centering
\captionsetup{justification=centering}
	\begin{tabular}{ c | c | c }
	\toprule
	& \textbf{Simulation with}  	   & \textbf{Simulation with}        \\
	& \textbf{theoretical}  		   & \textbf{recalibrated }			 \\
	\multirow{-3}{*}{\textbf{Symbol}}
	& \textbf{parameters}			   & \textbf{parameters} 			 \\
	\midrule
	$Q$                       & 50.0                  & 30.0 		  	\\  
	$f_0$                     & 47.0 Hz               & 27.9 Hz  		\\
	$x_0$                     & 0.49 mm               & 0.50 mm    		\\
	$K$                       & 2.56e5 N/m            & 0.85e5 N/m 		\\
	${k^2_{sys}}$             & 8.72 \%               & 1.25 \% 		\\
	$\eta_{bo}$               & 79 \%                 & 12.9 \%   		\\
	\bottomrule
	\end{tabular}
	\caption{Theoretical and experimentally recalibrated values of the electromechanical converter.}
	\label{tab:parametres_lacher_free}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%

    %///////////////////////////////////////////// 
	\subsection{The HV hydraulic behavior}	
	\label{The hydraulic valves}
    %/////////////////////////////////////////////

	%/////////////////////////////////////////////
	\subsubsection{Test bench presentation}
	 %/////////////////////////////////////////////

	%/////////////////////////////////////////////
	\subsubsection{Results and discussion}
    %/////////////////////////////////////////////
